\vspace*{-2.5cm} \hspace*{-0.5cm}Online platformazation and Offline expansion of Real Estate Brokerage: Evidence from China\footnote{ We are grateful for various people from various university, and several conferences for useful feedback. }

### 2024-07-04 manuscript/main.tex
modified:   manuscript/main.aux 	modified:   manuscript/main.fdb_latexmk 	modified:   manuscript/main.fls 	modified:   manuscript/main.log 	modified:   manuscript/main.out 	modified:   manuscript/main.pdf 	modified:   manuscript/main.synctex.gz 	modified:   manuscript/main.tex 	modified:   network_estimation/network_structure.ipynb 	modified:   result_tables/clustering_indices.tex

\begin{equation}
  Y_{it} = \beta_0 + \beta_1 density_{it} + \bf{\alpha} \bf{X}_{it} + \tau_{it} + \mu_i + \epsilon_{it}, \label{eq:multi-way-fe}
\end{equation}

where $Y_{it}$ is the three main dependent variables, including $\log(\text{number})$, price concession, and $\log(\text{lead times})$, $density_{it}$ is the DBI, $\bf{X}_{it}$ is a set of control variables, including brokerage\_control Lag(hedonic\_control), transaction\_control and region\_control, while $\tau_{it}$ is the time dummy variable interacting with the fixed effect of the business area, $\mu_i$ is the neighborhood fixed effect and $\epsilon_{it}$ is the random error term. The standard errors are clustered at the each business area level.\footnote{The business area is defined as a combination of multiple neighborhoods, which Lianjia designates as the primary divisions of the entire region.} The results are shown in Table \ref{tab:stylized_fact}.

@@

\begin{equation}
    Y_{it} = \beta_0 + \rho Y_{it-1} + \sum_{i=2}^7 density_{it} * year_{it} + \bf{\alpha} \bf{X}_{it} + \tau_{it} + \mu_i + \epsilon_{it}. \label{eq:dynamic}
\end{equation}

@@

\begin{equation}
    Y_{it} = \beta_0 +  \beta_1 pre_2 + \beta_2 entry + \beta_3 post_1 + \beta_4 post_2 + \beta_5 post_3 + \bf{\alpha} \bf{X}_{it} + \tau_{it} + \mu_i + \epsilon_{it}.   \label{eq:entry_effect}
\end{equation}

@@

\begin{equation}
  \begin{aligned}
    Y_{it} & = \beta_0 + \beta_1 \text{prev\_treatment}_{it} + \beta_2 \text{treatment}_{it} + \sum_{j=3}^5 \beta_{i} \text{post\_j\_treatment}_{it} + \\
           & \bf{\alpha} \bf{X}_{it} + \tau_{it} + \mu_i + \epsilon_{it}. \label{eq:acn_assessment}
  \end{aligned}
\end{equation}

@@

@@

@@

We then calculated the network clustering effect for each neighborhood using Breadth First Search Algorithm (BFS) described in the Algorithm \ref{alg:clustering_effect}:

@@

% need to refine
This approach allows us to quantify the local clustering effect within the segmented market and assess its impact on neighborhoods. This connection is in line with the reality in that firstly, cooperation between stores to complete a transaction is very common, and more stores within the segmented market can contributed more to the transaction as more efforts can be jointly made between different agents. Secondly, the influence of the netowrk decays from subconnected nodes and this is due to the decreasing benefits by connecting other sub-connecting.

Following the Lianjia's platform consolidation strategy, Lianjia decided to consolidate downstream brokerages to form a larger clustering within the segmented market and increase. By attracting other brokerage's into the network will initially make the brokreage's profit down because attracting other people in the platform meaning the market share would be decreased due to the intense competition. However, after the setup of the platform, the market will be more productive and more competitive to occupying a larger share of the whole network. This mechanism is more likely to get better control over the listing and people are more willing to list their house on this platform. Then according to the this would be resulted in a winners-take-all market.

In this case, we need to empirically estimate the spillover effect, and if this spillover effect is significant in this setting then people's reaction

To set up, we first match the brokerages' with the

We decided to use the so called quantile estimator described in model  proposed by \citep{machado_quantiles_2019}.

\begin{equation}
  \begin{aligned}
    Q_y(\xi \mid X) & = \beta_0 + \beta_1(\xi) \text{pre\_treatment}_{it} + \beta_2(\xi) \text{treatment}_{it} + \sum_{i=3}^5 \beta_i(\xi) \text{post\_treatment}_{it} \\
    & + \beta(\xi) \bf{X}_{it} + \mu_i + \tau_t + \varepsilon_{it}
  \end{aligned}
\end{equation}

\ref{tab:quantile_estimate_network} shows the quantile estimation of the . We can see that the

@@

The Chinese real estate market witnessed a significnat drop at 2022 and the labor market is fierece in recently and therefore, the people are pretty hard to get on jobs.

>>>>

\begin{equation}
  Y_{it} = \beta_0 + \beta_1 density_{it} + \bf{\alpha} \bf{X}_{it} + \eta_{t} \times \text{bs\_code}_i + \mu_i + \epsilon_{it}, \label{eq:multi-way-fe}
\end{equation}

where $Y_{it}$ is the three main dependent variables, including $\log(\text{number})$, price concession, and $\log(\text{lead times})$, $density_{it}$ is the DBI, $\bf{X}_{it}$ is a set of control variables, including brokerage\_control Lag(hedonic\_control), transaction\_control and region\_control, while $\eta_{t} \times \text{bs\_code}_i$ is the time dummy variable interacting with the fixed effect of the business area, $\mu_i$ is the neighborhood fixed effect and $\epsilon_{it}$ is the random error term. The standard errors are clustered at the each business area level.\footnote{The business area is defined as a combination of multiple neighborhoods, which Lianjia designates as the primary divisions of the entire region.} The results are shown in Table \ref{tab:stylized_fact}.

@@

\begin{equation}
  Y_{it} = \beta_0 + \rho Y_{it-1} + \sum_{i=2}^7 density_{it} * year_{it} + \bf{\alpha} \bf{X}_{it} + \eta_{t} \times \text{bs\_code}_i + \mu_i + \epsilon_{it}. \label{eq:dynamic}
\end{equation}

@@

\begin{equation}
  Y_{it} = \beta_0 +  \beta_1 pre_2 + \beta_2 entry + \beta_3 post_1 + \beta_4 post_2 + \beta_5 post_3 + \bf{\alpha} \bf{X}_{it} + \eta_{t} \times \text{bs\_code}_i + \mu_i + \epsilon_{it}.   \label{eq:entry_effect}
\end{equation}

@@

\begin{equation}
  \begin{aligned}
    Y_{it} & = \beta_0 + \beta_1 \text{prev\_treatment}_{it} + \beta_2 \text{treatment}_{it} + \sum_{j=3}^5 \beta_{i} \text{post\_j\_treatment}_{it} + \\
           & \bf{\alpha} \bf{X}_{it} + \eta_{t} \times \text{bs\_code}_i + \mu_i + \epsilon_{it}. \label{eq:acn_assessment}
  \end{aligned}
\end{equation}

@@

\subsection{Measure of Network Effect} \label{subsec:measure_network_effect}

@@

From Table \ref{tab:local_global_clustering_indices}, we observe a general increasing trend in the network effects during the study period, with some cities exhibiting more pronounced network effects than others. However, it is important to note that no city demonstrates a particularly strong network effect throughout the research period; the network effects remain moderate. This suggests that the observed network structure is characterized by local clustering rather than extensive global connectivity, consistent with our graphical observations. Moreover, Lianjia's network effects exhibit similar patterns in terms of local clustering indices across different cities. However, the overall connectivity, as indicated by the global clustering index, varies significantly among cities. For instance, Guangzhou has a global clustering index of 0.56, indicating a very high level of overall connectivity. This contrast highlights the heterogeneous nature of network structures across different urban markets.

@@

To calculate the network effect on the neighborhoods in the graph, we then calculated the network clustering effect for each neighborhood using Breadth First Search Algorithm (BFS) described in the Algorithm \ref{alg:clustering_effect}:

@@

% need to refine
This approach allows us to quantify the local clustering effect within the segmented market and assess its impact on neighborhoods. The average effect of the network is [] and the standard deviation is []. This connection is in line with the reality in several ways. Firstly, cooperation between stores to complete a transaction is very common, and having more stores within the segmented market can contribute significantly to the transaction process as more efforts can be jointly made by different agents. The collaboration between agents enhances the efficiency and effectiveness of the transaction process, leading to potentially quicker sales and better matching between buyers and properties. Secondly, the influence of the network decays with distance from subconnected nodes. This is due to the diminishing benefits of connecting with more distant nodes, as the value of information decreases with increasing distance. Information shared over longer distances may lose relevance or accuracy, thereby reducing its appeal and utility in facilitating transactions. Thirdly, we disregard each neighborhood's influence from other neighborhoods. This assumption is consistent with the observation that most houses within a neighborhood share similar characteristics, and the transaction effects within one neighborhood do not significantly impact other neighborhoods. Lastly, following Lianjia's platform consolidation strategy, the company decided to consolidate downstream brokerages to form larger clusters within the segmented market. This strategy primarily focuses on enhancing the connectivity and collaboration among stores within the network. To assess the impact of this strategy, we can examine the effects at the neighborhood level, as the increased cooperation among stores is expected to influence local market dynamics. By analyzing the neighborhood-level effects, we can better understand how the consolidation of brokerages translates into improved transaction efficiency and enhanced network effects, thereby reflecting the overall success of the platform consolidation strategy.

\subsection{Estimation of Network Consolidation on Network Effect} \label{subsec:platform_network_effect}

To empirically estimate the impact of network consolidation on the network effect, we also consider the influence of Lianjia's platform consolidation strategy on the local network clustering effect for each neighborhood. This strategy primarily targets Lianjia's offline stores, and its impact is likely to be heterogeneous across different neighborhoods. Specifically, neighborhoods that already had a diverse range of stores within the network before the strategy's implementation are expected to experience a more pronounced effect. Conversely, in neighborhoods where the local network effect was initially weak, the strategy's influence is expected to be relatively limited.

In this context, a DID estimator can be employed to evaluate the average treatment effect. However, given the dynamic nature of the strategy's implementation across different periods, the traditional DID approach may not fully capture the varying impacts. Therefore, we employ a quantile regression estimator, as described in the model proposed by \citep{machado_quantiles_2019}, to better understand the distributional effects of the strategy. The quantile regression approach allows us to analyze the impact of the platform consolidation strategy across different points in the distribution of the local network clustering effect. This method provides a more nuanced understanding of how the strategy affects neighborhoods differently, capturing both the average treatment effect and the variability in effects across the distribution. The model is described as the follows:

\begin{equation}
  \begin{aligned}
    Q_y(\tau \mid X) & = \beta_0 + \beta_1(\tau) \text{Pre\_Treatment}_{it} + \beta_2(\tau) \text{Treatment}_{it} + \sum_{j=3}^5 \beta_j(\tau) \text{Post\_j\_Treatment}_{it} \\
                     & + \alpha(\tau) \bf{X}_{it} + \mu_i + \eta_t + \epsilon{it}
  \end{aligned}
\end{equation}

where $Q_y(\xi \mid X)$ represents the $\tau$-th quantile of the dependent variable $y$ given the predictors $X$, where $\tau \in \{5, 10, \ldots, 95\}$. $\beta_0$ is the intercept term, $\text{Pre\_Treatment}_{it}$ is a dummy variable indicating the pre-treatment period, $\text{Treatment}_{it}$ is a dummy variable indicating the treatment group in 2018 and $\text{Post\_j\_Treatment}$ is a set of dummy variables indicating the post treatment group interacting with that year. $\mu_i$ represents individual fixed effects and $\eta_t$ is the year fixed effect and $\epsilon_{it}$ is the error term. To eliminate potential biases arising from nodes that are perpetually isolated from the network, such as neighborhoods with very few listings, we have decided to exclude samples that do not have any connections with other nodes. The results are reported in Table \ref{tab:quantile_estimate_network}.

Table \ref{tab:quantile_estimate_network} presents the quantile estimation results of the network clustering effect following the platform consolidation strategy. Prior to the treatment, the coefficients are not significant at the 10\% level, indicating no observable effect on the network clustering effect and no observatory changes before the effect. In the first period after the platform consolidation strategy's implementation, the influence on the lowest 5\% quantile of the network is not significant at the 10\% level. However, there is a significant increase in network clustering, with a coefficient of 0.86, though the magnitude of this effect decreases as the quantile level increases. This suggests that the platform consolidation strategy has a more pronounced impact on neighborhoods with initially lower network clustering, facilitating the formation of larger and more connected networks.

The effect of the strategy continues to grow in magnitude in the first period post treatment groups, with coefficients increasing from 1.1 to 1.4 across the quantiles. This trend intensifies in the second period, with even greater changes observed in network clustering, indicating an escalating impact over time. This pattern is consistent with the intuition that the platform consolidation strategy enhances network effects by forming larger clusters within the segmented market, thereby improving transaction efficiency and market competitiveness. In the final period of the study, the trend in magnitude begins to shift. The strategy's effect becomes significant for already well-connected groups rather than for those with initially low connectivity. This indicates that the consolidation strategy continues to strengthen existing networks, making well-connected neighborhoods even more integrated and efficient.

Overall, the results suggest that the platform consolidation strategy has a significant and dynamic impact on the network clustering effect. Initially, it benefits neighborhoods with lower connectivity, helping them to form larger and more efficient clusters. Over time, the strategy's influence extends to enhance the clustering of already well-connected neighborhoods, thereby continuously improving the overall network structure and market performance. Moreover, from the long-term perspectives, the online consolidation effect is beneficial for Lianjia's competitiveness because the larger the local network effect, the better Lianjia can better can have better contorl in the information. Moreover, from a long-term perspective, the online consolidation effect enhances Lianjia's competitiveness, as a stronger local network effect enables Lianjia to exert greater control over information.

@@

The Chinese real estate market witnessed a significant drop at 2022 and the labor market is fierece in recently and therefore, the people are pretty hard to get on jobs.
